TBD

### 2016-08-31 paper/paper.tex
typo

We are interested in the stability of closed loop systems, i.e., controllers along with a
model of their physical environment, the plant, as shown in Fig.~\ref{fig:closed-system}.

@@

  \path[->] (aux0) edge (circle.west);
  \path  
   (circle.east) edge (da.west)
   (da.east) edge (p.west)
   (p.east) edge (ad.west)
   (ad.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (c.east)
   (c.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed Loop System. \label{fig:closed-system}}
\end{figure*}

@@

\paragraph{Stability analyses of closed loop systems} 
In \cite{DBLP:conf/hybrid/RouxJG15}, the authors
perform the analysis in the state space
domain using Lyapunov-based quadratic invariants.
In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al. 
design a control software verification framework for gas turbine engines.

>>>>

We are interested in the stability of closed-loop systems, i.e., controllers along with a
model of their physical environment, the plant, as shown in Fig.~\ref{fig:closed-system}.

@@

  \path[->] (aux0) edge (circle.west);
  \path  
   (circle.east) edge (da.west)
   (da.east) edge (p.west)
   (p.east) edge (ad.west)
   (ad.east) edge (aux1.west)
   (aux1.south) edge (aux2.north)
   (aux2.west) edge (c.east)
   (c.west) edge (aux3.east); 
  \path[->]  (aux3.north) edge (circle.south);
 \end{tikzpicture}
}
 \caption{Closed-Loop System. \label{fig:closed-system}}
\end{figure*}

@@

\paragraph{Stability analyses of closed-loop systems} 
In \cite{DBLP:conf/hybrid/RouxJG15}, the authors
perform the analysis in the state space
domain using Lyapunov-based quadratic invariants.
In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al. 
design a control software verification framework for gas turbine engines.
